\sys: Automated Data-Parallel Shell Processing

### 2020-05-03 pldi/draft.tex

\TODO{Talk about the importance of eagerness and why we need to
  enforce it to get benefits. Discuss the necessity of having files as
  buffers and how we addressed the issue of cat's lazy consumption of
  its inputs.}

@@

\kk{Ideally we would want to talk here about the as-late-as possible
  dish translation that allows us to be safe despite the Shell's
  dynamic nature. I think that this is a great point about the
  work. Maybe we should also focus on implementing it before the OSDI
  deadline.}

@@

\TODO{Explain the plots with eager/no-eager as follows. Say that we
  initially decided to only make an eager version of cat (to allow for
  parallelism). However, we saw that results are still not good, so we
  resorted to making a proper generic eager node that can be put
  anywhere in the graph and that eagerly consumes its input. The above
  results show the improvement with it. Rerun them with eager only
  before cat in the no eager cases so that the minimal-grep example is
  the same with and without our eager node. (Maybe) we need to mention
  that eager has disk usage overhead that is linear to the size of the
  pipeline and the size of the input.}

>>>>

@@

%% \kk{Ideally we would want to talk here about the as-late-as possible
%%   dish translation that allows us to be safe despite the Shell's
%%   dynamic nature. I think that this is a great point about the
%%   work. Maybe we should also focus on implementing it before the OSDI
%%   deadline.}

@@

%% \TODO{Explain the plots with eager/no-eager as follows. Say that we
%%   initially decided to only make an eager version of cat (to allow for
%%   parallelism). However, we saw that results are still not good, so we
%%   resorted to making a proper generic eager node that can be put
%%   anywhere in the graph and that eagerly consumes its input. The above
%%   results show the improvement with it. Rerun them with eager only
%%   before cat in the no eager cases so that the minimal-grep example is
%%   the same with and without our eager node.}

\TODO{(Maybe) we need to mention that eager has disk usage overhead
  that is linear to the size of the pipeline and the size of the
  input.}
